Estimating duration in the presence of misclassification

### 2024-03-29 cis-perf-new-ll.tex
Finish new likelihood sketch

@@

Just a sketch, probably ignore for now.

\begin{itemize}
  \item Add $\vec{y}_j$ as the observed test results for episode $j$ to $O(j)$ (as defined previously).
  \item Modify $p_k$ and $p_u$ as done currently.
\end{itemize}

>>>>

\subsubsection{Deriving $p_k$}

Decompose $p_k$ as $p_k = \prob(O(j) = \nu_k \mid \vec{\theta}) = p_{ik} \prob(i(j) = i_k \mid \vec{\theta})$ where $p_{ik} = \prob(O(j) = \nu_k \mid i(j) = i_k, \vec{\theta})$.
This is valid as $\prob(O(j) = \nu_k \mid i(j) \neq i_k) = 0$ due to the condition here being equivalent to equating the two vectors' final elements.
Assume that each infection episode occurs independently and with equal probability in any individual, \ie $\prob(i(j) = i_k) = 1/\Ncis$ for all $j$ and $k$.

Then the derivation for $p_{ik}$ proceeds as per the derivation for $p_{ia}$ in the original version, except replacing $j(i)$s with $k$s.

@@

Similarly, let $p_k'$ and $p_{ik}'$ have the same definition as $p_k$ and $p_{ik}$ except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$.
